---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"binomial"` is a minimal [R](http://www.r-project.org/) package 
that provides functions for calculating probabilities of a Binomial random variable, and related calculatiion such as the probability distribution, the expected values, variance, etc.

* `bin_choose()` function calculates the number of combinations in which k successes can occur in n trials.
* `bin_probability()` function calculates the probability of getting successes in trials with probability prob per trial.
* `bin_distribution()` function calculates the probability distribution and return a binomial distribution object "`bindis`".
* `plot.bindis()` function graphs a barplot to display the probability histogram of a binomial distribution object "`bindis`".
* `bin_cumulative()` function calculates the cumulative distribution and return a binomial distribution object "`bincum`".
* `plot.bincum()` function graphs a barplot to display the cumulative distribution of a binomial distribution object "`bincum`".
* `bin_variable()` function shows the information about variables and return a binomial distribution object "`binvar`".
* `print.binvar()` function prints the content of an object "`binvar`".
* `summary.binvar()` function provides a full summarty description of an object "`binvar`" and return an oject "`summary.binvar`".
* `print.summary.binvar` function prints the contents of an object "`summary.binvar`".
* `bin_mean()` function calculates the `mean` of binomial distribution.
* `bin_variance()` function function calculates the `variance` of binomial distribution.
* `bin_mode()` function function calculates the `mode` of binomial distribution.
* `bin_skewness()` function function calculates the `skewness` of binomial distribution.
* `bin_kurtosis()` function function calculates the `kurtosis` of binomial distribution.


## Motivation

This package has been developed to illustrate some of the concepts
behind the creation of an R package.

## Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
# install.packages("devtools") 
# install "binomial" (without vignettes)
devtools::install_github("stat133-sp19/hw-stat133-AliceQiuhy/binomial")
# install "binomial" (with vignettes)
devtools::install_github("stat133-sp19/hw-stat133-AliceQiuhy/binomial", build_vignettes = TRUE)
```

## Usage

```{r}
library(binomial)

## bin_choose()
bin_choose(n = 5, k = 2)

#bin_probability()
bin_probability(2,5,0.5)

#bin_distribution()
dis1 <- bin_distribution(trials = 5, prob = 0.5)
dis1
plot(dis1)

# bin_distribution()
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
dis2
plot(dis2)

# bin_variable()
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
binsum1 <- summary(bin1)
binsum1

#Function of measures
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```
