---
title: "Introduction to Package binomial"
author: "Haoyi Qiu"
date: "4/28/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Package binomial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial distribution 

The package `bimonial` implements functions for calculating probabilities of a Binomial random variable, and related calculatiion such as the probability distribution, the expected values, variance, etc. 

## Function `bin_choose`

Function `bin_choose` calulates the number of combinations in which k success can occur in n trials.

```{r}
bin_choose(n = 5, k = 2)
```

## Function `bin_probability`

Function `bin_probability` calculates the probability of the given successs and trials. 

```{r}
bin_probability(2,5,0.5)
```

## Function `bin_distribution`

Function `bin_distribution` shows the binomial probability distribution.

```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
dis1
plot(dis1)
```

## Function `bin_cumulative`

Function `bin_distribution` shows the binomial cumulative distribution.

```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
dis2
plot(dis2)
```

## Function `bin_variable`

Function `bin_variable` calculates the summary measures.
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
binsum1 <- summary(bin1)
binsum1
```
